Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.3.3)

### 2016-01-24 MSstats_v3/MSstats_manual_RMarkdown.Rmd
2016.01.23 - v3.3.3.1

---
title: "Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.3.2)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "January 21, 2016"
output: pdf_document
bibliography: bibliography.bib
---

@@

```{r, eval=F}
install.packages(pkgs = 'MSstats_3.3.2.tar.gz', repos = NULL, type = 'source')
```

@@

@@

##### Profile plots

@@

>>>>

---
title: "Protein significance analysis of mass spectrometry-based proteomics experiments with R and MSstats (v3.3.3)"
author: "Meena Choi, Tsung-Heng Tsai & Erik Verschueren"
date: "January 23, 2016"
output: pdf_document
bibliography: bibliography.bib
---

@@

```{r, eval=F}
install.packages(pkgs = 'MSstats_3.3.3.tar.gz', repos = NULL, type = 'source')
```

@@

#### 4.2.1.3 Feature selection options

`MSstats` supports several options for selecting features. `featureSubset="all"`(default) uses all features that the data set has. `featureSubset="top3"` uses top 3 features which have highest average of log2(intensity) across runs. `featureSubset="highQuality"` removes the features with interference.

With `featureSubset="highQuality"`, the proteins can loss all features and be removed for next analysis, if all features are highly interfered. `remove_proteins_with_interference=TRUE` allows the algorithm to remove the proteins if deem interfered. `remove_proteins_with_interference=FALSE` (default) does not allow to remove the proteins, in which all features are interfered. In this case, the proteins, which will completely loss all features by the algorithm, will keep the most abundant peptide.

```{r, eval=F, message=F, warning=F}
DDA2009.TMP.featureselection <- dataProcess(raw = DDA2009.superhirn,  fillIncompleteRows = TRUE,
                                            normalization = 'equalizeMedians',
                                            featureSubset = 'highQuality',
                                            remove_proteins_with_interference = FALSE,
                                            summaryMethod = 'TMP',
                                            censoredInt = "NA", cutoffCensored = "minFeature",
                                            MBimpute = TRUE)

```

@@

@@

#### 4.2.2.3 Feature selection effects

Profile plots show the features after removing the featuares with interference.

```{r, eval=F}
dataProcessPlots(data = DDA2009.TMP.featureselection, type="Profileplot",  ylimUp=35,
                 featureName="NA", width=7, height=7, address="DDA2009_feature_selection_")

```

![](/Users/Meena/Dropbox/MSstats_GitHub_document/MSstats_v3/DDA2009_feature_selection_ProfilePlot_yeast.png)

![](/Users/Meena/Dropbox/MSstats_GitHub_document/MSstats_v3/DDA2009_feature_selection_ProfilePlot_wSummarization_yeast.png)
